Viscous Erosion in Porous Media

### 2018-03-20 docs/methods/erosion_methods.tex
toned down the intro

Another application, which motivates the current work, is erosion caused by groundwater flow.
Here, a slow moving fluid erodes channels in the ground, and this
affects the fluid transport.  In all these examples, there is a feedback
process between the flow and the eroding bodies---the shape of the
bodies affect the flow, while the flow changes the shape by fluidizing
each body.  This fluid-mechanical feedback system has been simulated in
idealized cases such as a single eroding two-dimensional body in a
uniform flow~\cite{moo-ris-chi-zha-she2013} or a single mobile eroding
three-dimensional body~\cite{mit-spa2016}. However, to better understand
the effect of erosion on groundwater flow, multiply-connected domains
must be considered.  Here we simulate two-dimensional erosion, in
multiply-connected domain such as the porous geometry of many
groundwater flows (Fig.~\ref{fig:50bodies}).

Because of the length and velocity scales of groundwater flow, we
restrict our attention to small Reynolds number flows.  For groundwater
flow, Darcy's law is often used, but this does not resolve the pore
structure and assumes a homogeneous geometry which is often not valid.
Instead, we use the incompressible Stokes equations to represent the
flow, and the individual pores are resolved which results in a complex
multiply-connected geometry.  A boundary integral equation (BIE) is
well-suited for solving the incompressible Stokes equations in a complex
geometry since it can resolve individual grains and the non-negligible
interactions between bodies are resolved. Moreover, high-order accuracy
and computational efficiency are obtained. To link the eroding body and
fluid dynamics, the body is eroded in the normal direction at a rate
that is proportional to the magnitude of the shear
stress~\cite{ris-moo-chi-she-zha2012}.  However, tracking the interface of
fluid-structure interaction problems with a long time horizon is
particularly difficult---the mesh is often distorted and tangled by the dynamics
and regions of high curvature develop.  These two issues are resolved
by, first, introducing a tangential velocity field to maintain a grid
that is equispaced in arclength, but that does not affect the dynamics,
and, second, a curvature penalization term.  Furthermore, the frame of
reference is changed to \thL~variables so that the curvature term
appears as a diffusive term that can easily be handled in a 
numerically stable fashion, e.g.~via an exponential integrator or an implicit method.

In addition to simulating the eroding grains, the flow is further
characterized by computing the vorticity in the flow.  The vorticity is
particularly insightful since it is identical to the shear stress on
no-slip boundaries.  Therefore, by computing the
vorticity, we are able to locate regions where the erosion rates will be
fastest or slowest.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions} The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
Since groundwater flow occurs at small spatial and velocity scales, we
assume the flow is viscous (ie.~zero Reynolds number).  By allowing for
complex multiply-connected domains, we capture the effect that
interacting bodies have on erosion, and the grains in the flow are
individually resolved rather than homogenized.  We start by validating
our method on a single circular body placed symmetrically in a pipe
flow.  By artificially fixing the area of the body as a function of
time, we are able to characterize the long-time behavior of the shape
and the resulting flow and compare these results with analytical
results.  Then, we compute the vorticity of erosion in
multiply-connected geometries to better characterize erosion in porous
media.

@@

To create high-fidelity and computationally efficient numerical methods,
two fast and accurate methods are employed.  First, the fluid equations
and the erosion rate (shear stress) are efficiently solved with spectral
accuracy by using a fast-multipole-accelerated BIE method.  Given the
rate of erosion, the shape is integrated in time with second-order
accuracy.  All spatial derivatives are computed in Fourier space,
resulting in spectral accuracy in space.  To further visualize the
effect of erosion, we compute the vorticity of the flow
(Fig.~\ref{fig:50bodies}) to visualize regions of high and low erosion.

@@

%\todo[inline]{These are some of my thoughts on reworking this first paragraph. See if you like it.}
We begin by making two fundamental design choices: first, we restrict
ourselves to two spatial dimensions, and second the bodies are
considered immobile (i.e.~fixed to their initial locations). The
restriction to two dimensions allows us to simulate the erosion of many bodies
(up to $50$ in this manuscript) with high resolution, giving us the
ability to accurately characterize the erosion of a porous medium. While
BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible. The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation. While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.

%\todo[inline]{This is the original below:}
%There are two main limitations of the current
%work.  First, the flow is assumed to be two-dimensional.  However, by
%assuming that the flow is two-dimensional, we are able to simulate the
%erosion of more bodies and with higher resolution than would be
%available in three dimensions.  Moreover, several flows can be described
%to good accuracy under a two-dimensional approximation, but certain
%phenomena occur only in three dimensions.  Extending the current work to
%three dimensions is possible with a boundary integral equation
%formulation.  In particular, the fluid solvers exist~\cite{mal-bir2015},
%and the main challenges of a BIE solver have been addressed by other
%groups including surface representation~\cite{yin-bir-zor2006,
%vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
%kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
%ros-ols2015}.  The more significant challenge of extending our work to
%three dimensions is guaranteeing that the mesh does not become
%distorted, which can be done, for example, by using an extension of the
%two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.
%
%The second limitation is that the eroding bodies are fixed.  Mitchell
%and Spagnolie~\cite{mit-spa2016} simulate a single mobile eroding body
%in three dimensions~\cite{mit-spa2016}, but additional challenges are
%caused when there are multiple bodies. In particular, especially in
%dense suspensions, bodies can become extremely close to one another, and
%the interaction between the bodies is difficult to resolve unless the
%underlying mesh is refined to levels that are intractable. In future
%work we plan to consider mobile eroding bodies by including a small
%force and torque to prevent unphysical contact~\cite{lu-rah-zor2017}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Related work} Simulating eroding bodies has been studied
analytically, experimentally, and numerically.  Because of the scales
involves with geophysical flows, most of these works consider high
Reynolds number flows.  For instance, the experimental work of Moore et
al.~\cite{moo-ris-chi-zha-she2013} considers on the order of $10^4$.
For low Reynolds number flows, Mitchell and Spagnolie~\cite{mit-spa2016}
use a BIE for the traction jump to simulate the erosion of a mobile body
in three dimensions, but they only consider single body.

The effect of erosion on a geometry is quite rich.  For instance, it has
been hypothesized and numerically observed that the erosion leads to a
shear stress that is uniform on the body which results in a uniform
erosion rate.  The shape that has a uniform shear stress is analyzed in
three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
which is an extension of the analysis done by Pironneau~\cite{pir1973}
to find a Stokesian drag minimizing shape.  However, the effect of
erosion on a porous media is less understood.  With the methods
developed in this paper, quantities such as the total drag across a
porous region as a function of time can be computed.

@@

Another numerical challenge with simulating erosion is that
corners develop at points where the shear stress vanishes.  There is recent work for solving
BIEs in geometries with corners by using
carefully chosen local expansions around each corner~\cite{rac-ser2017,
ser-rok2016} or panel-based graded meshes~\cite{hel2011,
gil-hao-mar2014, bre2012}.  The limitation of these methods is that they
require the corner's location, a non-uniform spaced mesh, and some of
the methods have a large condition number.  One solution is to use two
meshes---one for the quadrature the other for the interface tracking.
Then, interpolation between the two grids is required, and this is the
approach taken by Ojala and Tornberg~\cite{oja-tor2015}.  Instead of
using two grids and interpolation operators, we only require the uniform
grid by slightly modify the geometry to maintain sufficient regularity.
First, we add a regularization term to the shear stress to penalize
regions of high curvature.  Second, we apply a Gaussian filter to smooth
the absolute value of the shear stress before the body shape is updated.

Several groups consider the optimal body in a Stokes fluid that
optimizes some quantity.  For example, Pironneau~\cite{pir1973} found
the axisymmetric shape of a fixed volume body that minimizes drag is
similar to an American football with an opening angle of 60 degrees, and
this shape corresponds to a body with constant surface vorticity.  This
analysis is taken further by Montenegro-Johnson and
Lauga~\cite{mon-lau2015} where the optimal axisymmetric shape of fixed
surface area is computed.  We include a similar calculation for the
two-dimensional Stokes equations, and the resulting shape agrees with
our numerical solution.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
We start by defining the main variables used to model erosion.  We only
consider flows that are confined by a solid wall $\Gamma$ that encloses
$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.
On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively. Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies). Neglecting inertial forces, the dynamics of the fluid is
fully characterized by the position of the bodies $\xx_\ell(s,t) \in
\gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
$\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid
velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the
governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
&&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model},
\end{split}
\end{equation}
where $\Vn$ is the normal velocity of the interface and $\mu$ is the
fluid viscosity.  The outer wall is formed by rounding off the corners
of $[-3,3] \times [-1,1]$, and we enforce the Hagen-Poiseuille flow
\begin{align*}
  \UU(\xx) = \umax (1-y^2,0), \quad \xx \in \Gamma,
\end{align*}
where $U$ sets the maximum of the imposed Poiseuille flow. Often, we
will simply set $U=1$, but in some instances we change $U$ dynamically
to enforce that the pressure drop across the computational cell is
constant as bodies erode within it.  The boundary of the fluid domain is
$\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.  To
minimize the boundary effects of the inflow and outflow, we only place
bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.

@@

To perform the simulations, we freeze the geometry at each time step,
solve the incompressible Stokes equations, and then update the geometry
according to the erosion model.  The separation between these two
processes is justified since the time scale of erosion is much longer
than that of the flow.

%We use a quasi-static approximation.  That is, at each time step, we
%freeze the geometry, solve the incompressible Stokes equations, and then
%update the geometry according to the erosion model.  The two steps
%inside the red rectangle describes a time step in the quasi-static
%approximation.
%\todo[inline]{Appeal to separation of scales to justify this quasi-static approximation; i.e.~the timescale of erosion is much longer than that of the flow.}

Our erosion model is based on the shear stress, and this model is
discussed in more detail in Section~\ref{sec:erosion}.  We then describe
how the incompressible Stokes equations are solved in $\Omega$ using a
boundary integral equation in Section~\ref{sec:bies}.  In
Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
in the geometry are avoided and perform a change of coordinates to treat a stiff term.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Erosion model} 
\label{sec:erosion}

Other models for erosion include ones that use an erosion rate that is
proportional to a power of the magnitude of the shear
stress~\cite{par-izu2000}, or ones that use a critical shear stress
below which erosion does not occur~\cite{lag2000}.

To model erosion, the normal velocity is  proportional to the absolute
value of the shear stress.   Since the constant of proportionality only
sets the time scale, we let $\Vn = |\tau|$ as described in
equation~\eqref{eqn:erosionModel}. For the sake of numerical stability,
we modify this law in Section~\ref{sec:thetaL}.

@@

In this section, we describe the boundary integral equations employed
for the fluid equations.  In particular, we recast the incompressible
Stokes equations with Dirichlet boundary conditions 
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega,
\end{alignat*}
into an equivalent BIE.  The boundary condition $\ff$ is the prescribed
velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.
Since we are interested in two dimensions, a stream function formulation
can be used by recasting the governing equations as a problem in
analytic function theory~\cite{gre-kro-may1996}.  So that our work can
extended to three dimensions, we instead use primitive variables by
writing the velocity in terms of the standard double-layer
potential~\cite{lad1963,poz1992}
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
density function.  As the viscosity $\mu$ also sets the time scale, we
take $\mu=1$.  \todo[inline]{Do you think we should flesh out this
time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$
(the erosion constant), what exactly is the timescale that defines our
dimensionless time.} \todo[inline]{This might be worth doing.  Is it
something you can do quickly or do you want me to take a crack at it?}

@@

>>>>

Another application, which motivates the current work, is erosion caused by groundwater flow.
Here, a slow moving fluid erodes channels in the ground, and this
affects the fluid transport.  To better understand
the effect of erosion on groundwater flow, multiply-connected domains
must be considered.  Here we simulate two-dimensional erosion, in
multiply-connected domain such as the porous geometry of many
groundwater flows (Fig.~\ref{fig:50bodies}).

Because of the length and velocity scales of groundwater flow, we
restrict our attention to zero Reynolds number flows.  For groundwater
flow, Darcy's law is often used, but this does not resolve the pore
structure and assumes a homogeneous geometry which is often not valid.
Instead, we use the incompressible Stokes equations as the governing
fluid equations, and the individual pores are resolved which results in
a complex multiply-connected geometry.  The dynamics of the individual
pores are modelled with an erosion model that where the erosion rate is
proportional to the magnitude of the shear stress.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions} The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
In this fashion, individual pores are resolved rather than
homogenized.  A boundary integral equation (BIE) is used to solve the
incompressible Stokes equations in the complex geometry.  We resolve
individual grains and the non-negligible interactions between bodies.
To link the eroding body and fluid dynamics, the body is eroded in the
normal direction at a rate that is proportional to the magnitude of the
shear stress.

To create high-fidelity and computationally efficient numerical methods,
two fast and accurate methods are employed.  First, the fluid velocity
and the erosion rate (shear stress) are efficiently computed with
spectral accuracy by using a fast-multipole-accelerated BIE method.  The
required spatial derivatives are computed with spectral accuracy in
Fourier space.  In addition to compute the shear stress, we also compute
the vorticity in the fluid bulk.  The vorticity is
particularly insightful since it is identical to the shear stress on
no-slip boundaries.  Therefore, by computing the vorticity, we are able
to locate regions where the erosion rates will be fastest or slowest
(Fig.~\ref{fig:50bodies}).

Once the erosion rate is computed, the shape is integrated in time with
second-order accuracy.  Tracking the interface of fluid-structure
interaction problems with a long time horizon is particularly
difficult---the mesh is often distorted and tangled by the dynamics and
regions of high curvature develop.  These two issues are resolved by,
first, introducing a tangential velocity field to maintain a grid that
is equispaced in arclength, but that does not affect the dynamics, and,
second, a curvature penalization term.  Furthermore, the frame of
reference is changed to \thL~variables so that the curvature term
appears as a diffusive term that can easily be handled in a numerically
stable fashion, e.g.~via an exponential integrator or an implicit
method.

We validate our method on a single circular body placed symmetrically in
a pipe flow.  By artificially fixing the area of the body as a function
of time, we are able to characterize the long-time behavior of the shape
and the resulting flow and these results agree with analytical results.
Then, we compute the vorticity of erosion in multiply-connected
geometries to better characterize erosion in porous media.

@@

@@

We begin by making two fundamental design choices: first, we restrict
ourselves to two spatial dimensions, and second the bodies are
considered immobile (i.e.~fixed to their initial locations). The
restriction to two dimensions allows us to simulate the erosion of many bodies
(up to $50$ in this manuscript) with high resolution, giving us the
ability to accurately characterize the erosion of a porous medium. While
BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible. The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation. While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Related work} Simulating eroding bodies has been studied
analytically, experimentally, and numerically.  Many of these works are
motivated by high Reynolds number geophysical applications, such as the
work of the second author~\cite{moo-ris-chi-zha-she2013,
ris-moo-chi-she-zha2012, moore2017riemann} and others~\cite{par-izu2000,
lag2000, coh-dev-sey-yi-szy-rot2015, han1969, Rothman2012,
hewett2017evolution, ristroph2018sculpting, lopez2018cfd,
lachaussee2018competitive, cohen2016erosion}.  The work most closely
related to ours simulates erosion in a three-dimensional incompressible
Stokesian fluid~\cite{mit-spa2016}, but they only consider single
eroding body.

The effect of erosion on a geometry is quite rich.  For instance, it has
been hypothesized and numerically observed that the erosion leads to a
shear stress that is uniform on the body which results in a uniform
erosion rate.  The shape that has a uniform shear stress is analyzed in
three dimensions by Montenegro-Johnson and Lauga~\cite{mon-lau2015}
which is an extension of the analysis done by Pironneau~\cite{pir1973}
to find a Stokesian drag minimizing shape.  In this idealized case,
analytical axisymmetric shapes that minimize the drag can be found.
However, the effect of erosion on a porous media is less understood.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
We start by defining the main variables used to model erosion.  We
consider flows that are confined by a solid wall $\Gamma$ that encloses
$M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The
bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write
$\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.  On each body, $\nn$ and
$\ss$ denote the unit normal and unit tangent vectors respectively.
Throughout the paper, we adopt the convention that $\ss$ points in the
counterclockwise direction and $\nn$ points out of the fluid domain
(i.e.~into the bodies). Neglecting inertial forces, the dynamics of the
fluid is fully determined by the position of the bodies $\xx_\ell(s,t)
\in \gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given
$\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid
velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the
governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
&&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model},
\end{split}
\end{equation}
where $\Vn$ is the normal velocity of the interface and $\mu$ is the
fluid viscosity.  The outer wall is formed by rounding off the corners
of $[-3,3] \times [-1,1]$, and we enforce the Hagen-Poiseuille flow
\begin{align*}
  \UU(\xx) = \umax (1-y^2,0), \quad \xx \in \Gamma,
\end{align*}
where $U$ sets the maximum of the imposed Poiseuille flow. Often, we
will simply set $U=1$, but in some instances we change $U$ dynamically
to enforce that the pressure drop across the computational cell is
constant as bodies erode within it.  The boundary of the fluid domain is
$\bd\Omega = \gamma_1 \cup \cdots \cup \gamma_M \cup \Gamma$.  To
minimize the boundary effects of the inflow and outflow, we only place
bodies in the center third, $[-1,1] \times [-1,1]$, of the fluid domain.

@@

There are several models for erosion that involve the shear
stress~\cite{par-izu2000,lag2000}.  The erosion model we adopt
prescribes that erosion occurs in the normal direction at a rate that is
proportional to the magnitude of the shear
stress~\cite{moo-ris-chi-zha-she2013}.  The constant of proportionality
only sets the time scale, so we let $\Vn = |\tau|$ as described in
equation~\eqref{eqn:erosionModel}.  For the sake of numerical stability,
we modify this law in Section~\ref{sec:thetaL}. To perform the
simulations, we freeze the geometry at each time step, solve the
incompressible Stokes equations, and then update the geometry according
to the erosion model.  The separation between these two processes is
justified since the time scale of erosion is much longer than that of
the flow.

We describe how the incompressible Stokes equations are solved in
$\Omega$ using a boundary integral equation in Section~\ref{sec:bies}.
In Section~\ref{sec:shearStressLP}, we discuss how the shear stress is
computed.  Finally, in Section~\ref{sec:thetaL}, we describe how corners
in the geometry are avoided and perform a change of coordinates to treat
a stiff term.

@@

In this section, we describe the boundary integral equations employed
for the fluid equations.  In particular, we recast the incompressible
Stokes equations with Dirichlet boundary conditions 
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega,
\end{alignat*}
into an equivalent BIE.  The boundary condition $\ff$ is the prescribed
velocity $\UU$ on $\Gamma$, and it is zero on the grains $\gamma$.  In
two dimensions, a BIE for a stream function formulation is
possible~\cite{gre-kro-may1996}, but this does not extend to three
dimensions.  Therefore, we adopt a primitive variable formulation where
the velocity is written in terms of the standard double-layer
potential~\cite{lad1963,poz1992}
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
density function.  As the viscosity $\mu$ also sets the time scale, we
take $\mu=1$.  \todo[inline]{Do you think we should flesh out this
time-scale stuff more precisely? i.e.~By setting $\mu = 1$ and $C = 1$
(the erosion constant), what exactly is the timescale that defines our
dimensionless time.} \todo[inline]{This might be worth doing.  Is it
something you can do quickly or do you want me to take a crack at it?}

@@

One challenge with simulating erosion is that corners develop at points
where the shear stress vanishes.  There is recent work for solving BIEs
in geometries with corners by using carefully chosen local expansions
around each corner~\cite{rac-ser2017, ser-rok2016} or panel-based graded
meshes~\cite{hel2011, gil-hao-mar2014, bre2012}.  The limitation of
these methods is that they require the corner's location, a non-uniform
spaced mesh, and some of the methods have a large condition number.  One
solution is to use two meshes---one for the quadrature the other for the
interface tracking.  Then, interpolation between the two grids is
required, and this is the approach taken by Ojala and
Tornberg~\cite{oja-tor2015}.  Instead of using two grids and
interpolation operators, we only require the uniform grid by slightly
modify the geometry to maintain sufficient regularity.  First, we add a
regularization term to the shear stress to penalize regions of high
curvature.  Second, we apply a Gaussian filter to smooth the absolute
value of the shear stress before the body shape is updated.
